Improving content discovery through combining linked data and data mining techniques

### 2015-12-05 report/report.tex
Got it compiling again.

$$
(IRI_1, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, IRI_2)
$$

@@

$$
(IRI, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, <\!\!http\!:\!\!//dbpedia.org/resource/Dog\!\!>)
$$

@@

$$
(IRI, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, <\!\!http\!:\!\!//dbpedia.org/resource/Animal\!\!>)
$$

@@

\begin{lstlistings}
  {
    ?article ex:takesPlaceIn ?city .
    ?city a ex:City .
    ?city ex:capitalOf ?country .
  } -> { ?iri ex:takesPlaceIn ?country }
\end{lstlistings}

\noident might be useful ot help cluster articles that take place in the same
country -- even if the countries are not always explicitly mentioned therein.
Such an inference requires knowledge about cities and countries to
write and domain experts for different types of content might be able to offer
more nuanced rules.

@@

$$
(IRI_1, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)
(IRI_2, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)
$$

In the RDF graph for IRI_2, say, we might find the source had provided an
\texttt{owl:sameAs} assertion such as:

$$
(ex2:anotherEntity, owl:sameAs, ex1:entity)
$$

@@

$$
(IRI_1, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)
(IRI_2, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)
(IRI_2, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)
$$

\noident and the feature generation stage might provide the common features
\texttt{dbprop_related_ex1_entity=true} for both content items.

@@

\begin{Maximal Data Pipeline}

>>>>

$$
(IRI_1, ex:related, IRI_2)
$$

@@

$$
(IRI, ex:related, ex:Dog)
$$

@@

$$
(IRI, ex:related, ex:Animal)
$$

@@

\begin{lstlisting}
  {
    ?article ex:takesPlaceIn ?city .
    ?city a ex:City .
    ?city ex:capitalOf ?country .
  } -> { ?iri ex:takesPlaceIn ?country }
\end{lstlisting}

\noindent might be useful ot help cluster articles that take place in the same
country -- even if the countries are not always explicitly mentioned therein.
Such an inference requires knowledge about cities and countries to
write and domain experts for different types of content might be able to offer
more nuanced rules.

@@

\begin{displaymath}
(IRI_{1}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)\\
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)
\end{displaymath}

In the RDF graph for $IRI_2$, say, we might find the source had provided an
\texttt{owl:sameAs} assertion such as:

\begin{displaymath}
(ex2:anotherEntity, owl:sameAs, ex1:entity)
\end{displaymath}

@@

\begin{displaymath}
(IRI_{1}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)\\
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex2:anotherEntity)\\
(IRI_{2}, <\!\!http\!:\!\!//dbpedia.org/property/related\!\!>, ex1:entity)
\end{displaymath}

\noindent and the feature generation stage might provide the common features
\texttt{dbprop\_related\_ex1\_entity=true} for both content items.

@@

\subsection{Maximal Data Pipeline}
